\chapter{Results}
\label{chap:05}
\setlength{\parskip}{1em}

\section{Machine Learning Model Evaluation}

\subsection{Lead Scoring Model Performance}

Model comparison was performed on the held-out 20\% test partition
(n~=~1,486~records). \Cref{tab:lead_results} reports the final test-set
metrics for all candidate models.

\begin{table}[H]
  \centering
  \caption{Lead scoring model comparison on test set}
  \label{tab:lead_results}
  \begin{tabularx}{\textwidth}{@{}L{3.8cm} C{1.5cm} C{1.5cm} C{1.5cm}
    C{1.5cm} C{1.6cm} C{1.6cm}@{}}
    \toprule
    \thead{Model} & \thead{Acc.} & \thead{Prec.} & \thead{Rec.} &
    \thead{F1} & \thead{AUC-ROC} & \thead{PR-AUC} \\
    \midrule
    Logistic Regression (baseline) &
      0.941 & 0.917 & 0.931 & 0.924 & 0.979 & 0.966 \\
    Random Forest &
      0.938 & 0.916 & 0.923 & 0.920 & 0.978 & 0.969 \\
    \textbf{HistGradientBoosting} (selected) &
      \textbf{0.949} & \textbf{0.935} & \textbf{0.933} &
      \textbf{0.934} & \textbf{0.983} & \textbf{0.974} \\
    XGBoost &
      0.948 & 0.929 & 0.935 & 0.932 & 0.982 & 0.969 \\
    \bottomrule
  \end{tabularx}
\end{table}

The HistGradientBoosting model was selected as the production lead
scoring model, achieving an F1-score of 0.934 and an AUC-ROC of 0.983
on the held-out test set, substantially exceeding the project
objectives of F1 $\geq$ 0.78 and AUC-ROC $\geq$ 0.80. The model also
achieved the highest PR-AUC (0.974), indicating strong performance on
the positive lead conversion class.

The lead conversion dataset contained behavioural, demographic, and
traffic-source attributes after removing identifier columns
(\texttt{Prospect ID} and \texttt{Lead Number}). Features used for
training included variables such as lead origin, lead source, time spent
on website, page visit frequency, activity history, occupation,
specialisation, and communication engagement indicators. Behavioural and
engagement-oriented variables are widely recognised as important
predictors of sales conversion and customer acquisition success
\citep{jolson1997,tsai2010}. The strong predictive performance of the
selected model therefore aligns with prior CRM and lead management
research showing that customer interaction behaviour provides valuable
signals for conversion likelihood.

\subsection{Churn Prediction Model Performance}

\begin{table}[H]
  \centering
  \caption{Churn prediction model comparison on held-out test set}
  \label{tab:churn_results}
  \begin{tabularx}{\textwidth}{@{}L{3.8cm} C{1.5cm} C{1.5cm} C{1.5cm}
    C{1.5cm} C{1.6cm} C{1.6cm}@{}}
    \toprule
    \thead{Model} & \thead{Acc.} & \thead{Prec.} & \thead{Rec.} &
    \thead{F1} & \thead{AUC-ROC} & \thead{PR-AUC} \\
    \midrule
    Logistic Regression (baseline) &
      0.754 & 0.525 & 0.765 & 0.622 & 0.841 & 0.632 \\
    Random Forest &
      0.722 & 0.486 & 0.837 & 0.615 & 0.821 & 0.616 \\
    \textbf{HistGradientBoosting (selected)} &
      \textbf{0.766} & \textbf{0.543} & \textbf{0.741} &
      \textbf{0.627} & \textbf{0.835} & \textbf{0.644} \\
    XGBoost &
      0.731 & 0.496 & 0.749 & 0.596 & 0.819 & 0.621 \\
    \bottomrule
  \end{tabularx}
\end{table}

The HistGradientBoosting classifier was selected as the production churn
prediction model based on its superior balance between discrimination
and classification performance on the held-out test set. The model
achieved an AUC-ROC of 0.835 and the highest PR-AUC of 0.644, while
also obtaining the best overall F1-score of 0.627. Compared with
Logistic Regression, Random Forest, and XGBoost,
HistGradientBoosting provided a more balanced trade-off between
precision (0.543) and recall (0.741), making it better suited for
identifying churn-prone customers while limiting false positives.

The churn prediction dataset consisted of customer demographic,
subscription, billing, and service usage attributes after removing the
unique identifier column (\texttt{customerID}). Features used for model
training included customer tenure, monthly and total charges, contract
type, payment method, internet service, technical support usage, online
security services, streaming services, and communication preferences.
Prior studies have consistently identified tenure, billing behaviour,
service quality, and contract structure as strong predictors of customer
retention and churn in telecommunications environments
\citep{huang2012,reichheld2001}. The selected model's ability to capture
non-linear interactions among these variables likely contributed to its
improved predictive performance over the baseline approaches.
