\chapter{Methodology}
\label{chap:03}
\setlength{\parskip}{1em}

\section{Research Framework}

This project adopts the Design Science Research (DSR) methodology as
formalised by \citet{hevner2004}. DSR comprises three interlocking cycles:

\begin{itemize}
  \item \textbf{Relevance cycle:} The project is grounded in an
  identifiable real-world problem (Section~1.2) and evaluated against
  practical requirements derived from that problem context.
  \item \textbf{Design cycle:} The artefact is constructed and refined
  through a structured phased development plan, with each phase evaluation
  informing subsequent design decisions.
  \item \textbf{Rigor cycle:} Design decisions are grounded in
  peer-reviewed knowledge bases documented in Chapter~2.
\end{itemize}

\section{Software Development Methodology}

A structured phased development model was adopted across a 20-week
project timeline. The model organises work into five sequential phases,
each with clearly defined inputs, outputs, and completion criteria.
\Cref{tab:phases} documents the phase plan and delivery status.

\begin{table}[H]
  \centering
  \caption{Project phase plan and delivery status}
  \label{tab:phases}
  \setstretch{1.1}
  \begin{tabularx}{\textwidth}{@{}L{3.0cm} C{1.6cm} X C{1.8cm}@{}}
    \toprule
    \thead{Phase} & \thead{Weeks} & \thead{Primary Deliverables} &
    \thead{Status} \\
    \midrule
    Phase 1: Requirements \& Design &
      1--2 &
      Requirements specification, technology selection, database schema,
      UML diagrams (use case, class, sequence) &
      Complete \\
    Phase 2: Backend Development &
      3--5 &
      FastAPI/SQLAlchemy project scaffold; authentication, contact, deal,
      and activity API modules; OpenAPI documentation &
      Complete \\
    Phase 3: ML Pipeline &
      6--7 &
      Data preprocessing pipeline, lead scoring model training and
      evaluation, churn prediction model training and evaluation,
      ML inference API endpoints with SHAP explanations &
      Complete \\
    Phase 4: Frontend \& Integration &
      7--8 &
      Vue.js~3 SPA, pipeline board, ML insight dashboard panels,
      end-to-end API integration, Docker packaging, Serverspace.io deployment &
      Complete \\
    Phase 5: Testing \& Documentation &
      9--10 &
      Unit and integration testing, load testing, technical
      documentation, paper writing &
      Complete \\
    \bottomrule
  \end{tabularx}
\end{table}
\section{Requirements Engineering}

Requirements were elicited through two methods: analysis of publicly
available feature lists, user reviews, and published documentation for the
five CRM systems examined in \cref{sec:existing_systems}; and review of
the existing literature on SME CRM adoption factors \citep{nguyen2013}.
Requirements were prioritised using the MoSCoW method.

\subsection{Functional Requirements (Must Have)}

\begin{itemize}
  \item[\textbf{FR-1}] The system shall support user registration, login,
  and role-based access control (Admin, Manager, Sales Representative).
  \item[\textbf{FR-2}] The system shall provide CRUD operations on
  Contacts, Companies, and Deals.
  \item[\textbf{FR-3}] The system shall implement a visual Kanban pipeline
  board for deal stage management.
  \item[\textbf{FR-4}] The system shall record Activities (calls, emails,
  meetings, notes) linked to Contacts and Deals.
  \item[\textbf{FR-5}] The system shall expose a lead scoring API endpoint
  returning a conversion probability and SHAP-based feature explanation.
  \item[\textbf{FR-6}] The system shall expose a churn prediction API
  endpoint returning a churn probability and risk tier.
  \item[\textbf{FR-7}] The system shall provide a dashboard displaying key
  sales metrics including pipeline value, stage conversion rates, and churn
  risk distribution.
  \item[\textbf{FR-8}] The system shall authenticate all API requests using
  JSON Web Tokens (JWT).
\end{itemize}

\subsection{Non-Functional Requirements}

\begin{itemize}
  \item[\textbf{NFR-1}] \textbf{Performance:} API response time less than
  500\,ms at the 95th percentile for standard CRUD operations under 100
  concurrent users.
  \item[\textbf{NFR-2}] \textbf{Availability:} 99.5\% uptime target on
  production infrastructure.
  \item[\textbf{NFR-3}] \textbf{Security:} Passwords hashed using bcrypt
  at a minimum cost factor of 12; HTTPS enforced on all endpoints; JWT
  tokens expire after 24~hours.
  \item[\textbf{NFR-4}] \textbf{Deployability:} The system shall be
  deployable on a Serverspace.io vStack VPS (Almaty) via Docker Compose
  with a documented step-by-step procedure requiring no prior DevOps
  expertise. All personal data shall remain within Kazakhstan.
  \item[\textbf{NFR-5}] \textbf{Maintainability:} Backend code coverage
  greater than or equal to 70\%; API documented via OpenAPI~3.0.
\end{itemize}

\section{Data Collection and Preparation}

Two publicly available datasets were used for ML model training and
evaluation in the absence of proprietary Kazakhstani SME CRM data.

\subsection{Lead Scoring Dataset}

A synthetic lead conversion dataset was derived from HubSpot's public
developer sandbox and sample API data \citep{hubspot_leads}, comprising
7,432 lead records with 18~features including lead source, industry,
company size, number of website visits, email open rate, number of calls
made, days since first contact, and a binary conversion label. The dataset
exhibits a 23.4\% positive-class rate, necessitating class balancing during
training.

\subsection{Churn Prediction Dataset}

The IBM Telco Customer Churn dataset \citep{ibmtelco}, publicly available
via Kaggle
(\url{https://www.kaggle.com/datasets/blastchar/telco-customer-churn}),
was employed for churn modelling. The dataset comprises 7,043 records with
21~features, with a churn rate of 26.5\%. Although the dataset originates
from a telecommunications domain, the underlying customer lifecycle dynamics
are structurally analogous to SME customer relationship data.

\subsection{Preprocessing Pipeline}

A unified preprocessing pipeline was implemented using scikit-learn's
\texttt{Pipeline} and \texttt{ColumnTransformer} abstractions:

\begin{itemize}
  \item \textbf{Missing value imputation:} Median imputation for continuous
  features; a designated \texttt{Unknown} category for nominal features.
  \item \textbf{Categorical encoding:} One-hot encoding for nominal features
  with ten or fewer categories; ordinal encoding for ordered features.
  \item \textbf{Numerical scaling:} \texttt{StandardScaler} applied for
  Logistic Regression; tree-based models required no scaling.
  \item \textbf{Class balancing:} SMOTE \citep{chawla2002} applied
  exclusively within training folds of cross-validation to prevent data
  leakage into the validation set.
\end{itemize}

\section{Model Development and Evaluation Protocol}

Both ML tasks were framed as binary classification problems. A systematic
model comparison was conducted using stratified 5-fold cross-validation on
the training partition (80\% of the full dataset), with a held-out 20\%
test set reserved for final one-time evaluation only. Hyperparameter
optimisation used \texttt{GridSearchCV} within the training folds.
Evaluation metrics included Accuracy, Precision, Recall, F1-Score,
AUC-ROC, and PR-AUC. SHAP TreeExplainer values were computed for the
selected production model in each task using the \texttt{shap} library
\citep{lundberg2017shap}.

