\chapter{Literature Review}
\label{chap:01}
\setlength{\parskip}{1em}

\section{Customer Relationship Management: Theoretical Foundations}

Customer Relationship Management as a formal discipline emerged from the
intersection of relationship marketing theory and enterprise information
systems in the early 1990s. The most widely cited academic definition is
provided by \citet{payne2005}, who characterise CRM as a strategic approach
concerned with creating improved shareholder value through the development
of appropriate relationships with key customers and customer segments. From
a systems perspective, CRM encompasses three functional dimensions:
operational CRM (the automation of sales, marketing, and service
processes), analytical CRM (the application of data warehousing and mining
to understand customer behaviour), and collaborative CRM (the
multi-channel coordination of customer interactions) \citep{buttle2019}.

\citet{buttle2019} further position CRM software as the technological
infrastructure that operationalises relationship marketing strategy,
cautioning that CRM value derives not from the software platform itself
but from the organisational processes and data discipline that accompany
implementation. This observation is consistent with the persistently high
CRM project failure rates reported in practitioner literature, where
40--70\% of implementations are estimated to fall short of their stated
objectives \citep{gartner2023crm}.

For SMEs specifically, \citet{nguyen2013} identify a distinct set of CRM
adoption success factors, finding that perceived ease of use,
top-management support, and cost-effectiveness are the principal
determinants of adoption in small business contexts. These findings
directly inform TinyCRM's design philosophy, which prioritises interface
simplicity, low configuration overhead, and total cost of ownership
optimisation.

\section{SaaS Architecture Patterns}

Software-as-a-Service delivery has become the dominant CRM deployment
model, with SaaS deployments comprising approximately 87\% of total CRM
implementations as of 2023 \citep{gartner2023crm}. The SaaS model affords
SMEs predictable subscription pricing, the elimination of on-premise
infrastructure costs, automatic updates, and ubiquitous browser-based
access.

From an architectural standpoint, SaaS applications must address
multi-tenancy, data isolation, horizontal scalability, and availability.
\citet{bezemer2010} classify multi-tenancy approaches on a spectrum from
simple hosting (shared nothing, one database per tenant) to true
multi-tenancy (shared schema with a tenant discriminator column). For an
MVP targeting a small initial user base, a single-tenant-per-deployment
model substantially reduces architectural complexity while preserving the
operational benefits of cloud hosting.

\citet{richardson2018} argues that while microservices architectures offer
scalability and team autonomy benefits, the operational complexity they
introduce is disproportionate for early-stage applications, and explicitly
recommends initiating development with a well-structured monolith. This
recommendation is directly adopted in TinyCRM's architectural
decision-making, as described in \cref{chap:design}.

\citet{fowler2014microservices} articulate the ``monolith first'' pattern:
construct a modular monolith whose internal boundaries correspond to future
microservice candidates, enabling extraction without complete rewrite.

\section{Platform-as-a-Service and Managed Deployment}

Modern PaaS providers substantially reduce the operational burden of
deploying web applications by abstracting server provisioning, TLS
certificate management, runtime detection, and continuous deployment
pipelines. \citet{serverspacedocs2025} confirm that Serverspace.io supports
deployment of applications via docker, that users have a simple control panel 
that allows a VPS to be created and accessible via SSH within 60~seconds. 
A vStack instance with 2~vCPU and 4~GB~RAM costs approximately USD~17 per 
month \citep{serverspacedocs2025}, which is accessible for student projects 
and early-stage SME deployments while providing dedicated resources rather 
than the shared-CPU environments typical of entry-level PaaS tiers. Critically 
for the Kazakhstani deployment context, the Almaty data centre is certified 
to ISO~9001 and PCI~DSS standards and satisfies Law~No.~94-V data residency 
requirements.

\section{Machine Learning for Lead Scoring}

Lead scoring, the prioritisation of sales prospects by estimated conversion
probability, has evolved from rule-based demographic heuristics to
ML-driven approaches capable of integrating behavioural signals.
\citet{baesens2002} demonstrates that ensemble methods, specifically
Gradient Boosting and Random Forest classifiers, consistently outperform
logistic regression and single decision trees across multiple industry
datasets, a finding subsequently replicated by \citet{chen2016xgboost}.

A critical insight from \citet{verbeke2012} is that raw predictive accuracy
is an insufficient criterion for evaluating business ML models:
interpretability is essential for sales team adoption and regulatory
accountability. This observation motivates the integration of SHAP values
\citep{lundberg2017shap} into TinyCRM's lead scoring API, providing
feature-level explanations alongside probability outputs.

Regarding feature importance, \citet{tsai2010} demonstrate that
behavioural engagement features (email open rates, call frequency, time
since last contact) have significantly higher predictive power than
demographic features when both sets are available. This finding is
reflected in TinyCRM's feature engineering specification, which centres
on interaction history derived from the activity log.

\section{Customer Churn Prediction}

Customer churn represents one of the most economically consequential
events in the customer lifecycle. The asymmetry between customer
acquisition cost and retention cost, estimated at a ratio of 5:1 to 7:1
in favour of retention \citep{reichheld2001}, makes churn prediction a
high-return machine learning application.

The methodological benchmark study by \citet{verbeke2012} demonstrates
that Random Forest and Gradient Boosting consistently achieve AUC-ROC
values in the range 0.82--0.89 on telecommunications churn benchmarks.
Logistic Regression retains practical value as an interpretable baseline,
particularly when feature engineering is thorough \citep{coussement2008}.

Class imbalance is a critical methodological challenge in churn modelling.
Standard mitigation strategies include SMOTE oversampling \citep{chawla2002},
cost-sensitive learning via class weighting, and decision threshold
calibration. TinyCRM's training pipeline applies SMOTE exclusively within
training folds during cross-validation to prevent data leakage.

\section{Analysis of Existing Systems}
\label{sec:existing_systems}
\setlength{\parskip}{1em}
%
A structured comparative analysis of five representative CRM platforms was
conducted to identify feature gaps pertinent to the Kazakhstani SME
context. The comparison criteria were drawn from the SME adoption factors
identified by \citet{nguyen2013} and supplemented with data sovereignty and
ML intelligence dimensions specific to this project's context.

\begin{table}[H]
  \centering
  \caption{Comparative analysis of existing CRM systems}
  \label{tab:crm_comparison}
%  \setstretch{1.2}
  \begin{tabularx}{\textwidth}{@{}L{2.4cm} L{2.2cm} L{2.2cm} L{2.4cm} L{2.4cm} L{2.4cm}@{}}
    \toprule
    \thead{System} & \thead{Architecture} & \thead{ML Features} &
    \thead{Pricing (\$user/mo)} & \thead{Data Location} &
    \thead{KZ Suitability} \\
    \midrule
    Salesforce Sales Cloud &
      Multi-tenant SaaS & Einstein AI (lead score, forecasting) &
      \$25--\$300 & US/EU (AWS) & Low \\[4pt]
    HubSpot CRM &
      Multi-tenant SaaS & Predictive score (Enterprise only) &
      \$0--\$150 & US (AWS) & Low \\[4pt]
    Bitrix24 &
      SaaS + on-premise & None native &
      \$0--\$199/org & EU / self-host & Medium \\[4pt]
    AmoCRM &
      Multi-tenant SaaS & None &
      \$15--\$45 & RU servers & Medium \\[4pt]
    SuiteCRM &
      Open-source, self-hosted & None &
      \$0 + hosting & Self-hosted & High \\[4pt]
    \textbf{TinyCRM} (this work) &
      Monolith SaaS & Lead score + churn (built-in) &
      \textasciitilde\$8--\$15 target & KZ (QazCloud) & High \\
    \bottomrule
  \end{tabularx}
\end{table}

The analysis reveals that no existing system simultaneously satisfies all
four Kazakhstani SME requirements: affordable pricing, personal data
localisation, native ML-driven predictive intelligence, and Kazakh-language
support. TinyCRM is explicitly positioned to address this gap.

\section{Summary and Research Gap}

The literature review establishes five foundational conclusions. First, CRM
is a well-theorised discipline with identifiable SME adoption success
factors centred on simplicity, cost, and perceived usefulness
\citep{nguyen2013}. Second, SaaS monolithic architectures are the
appropriate starting point for MVP-stage systems \citep{richardson2018,
fowler2014microservices}. Third, Gradient Boosting and Random Forest are
the state-of-the-art approaches for lead scoring and churn prediction
respectively \citep{verbeke2012, chen2016xgboost}. Fourth, model
interpretability via SHAP is a necessary complement to raw predictive
performance for business ML applications \citep{lundberg2017shap}. Fifth,
Serverspace.io (vStack, Almaty) provides a straightforward VPS deployment
path that satisfies both technical requirements and Kazakhstani data
residency obligations \citep{serverspacedocs2025,kazakhstanlaw94v}.
