\chapter{Discussion}
\label{chap:06}
\setlength{\parskip}{1em}

\section{Interpretation of Machine Learning Results}

The HistGradientBoosting model achieved an F1-score of 0.934 for lead 
scoring and an AUC-ROC of 0.983 on the held-out test set, placing it 
at the upper end of performance reported in comparable CRM predictive 
analytics literature. \citet{verbeke2012} report F1 values in the range 
of 0.79--0.88 for ensemble methods on similar binary classification 
problems, indicating that the TinyCRM model exceeds typical benchmark 
performance levels. The elevated recall (0.933) relative to 
precision (0.935) demonstrates a well-balanced operating point, 
indicating that the model maintains strong sensitivity to true conversion 
opportunities while keeping false positives under control. This balance is 
operationally appropriate in a CRM context, where missed high-value 
leads typically incur greater opportunity cost than additional review 
of low-probability leads.

The churn prediction model, based on HistGradientBoosting, 
achieved an AUC-ROC of 0.835 and an F1-score of 0.627. While the AUC-ROC 
is consistent with established benchmarks for churn prediction tasks 
in structured customer datasets, the F1-score reflects the inherent 
difficulty of class-imbalanced churn prediction, where positive churn 
events are relatively sparse. The PR-AUC of 0.644 provides a more 
informative measure of performance under class imbalance and indicates 
moderate but reliable precision at operational recall thresholds 
(approximately 0.6--0.75), where retention campaigns are typically triggered.

A critical qualification of both results is the use of non-Kazakhstani 
training data. Transfer to real Kazakhstani CRM environments may lead to 
performance degradation if customer behaviour patterns differ systematically 
from the training distribution. Potential sources of distribution shift 
include shorter sales cycles in SME segments, seasonality aligned with local 
fiscal and cultural calendars, and higher reliance on messaging-based 
communication channels such as WhatsApp that are not explicitly captured 
in the current feature set. This limitation motivates the incorporation of 
an active learning pipeline and periodic retraining strategy in the post-MVP 
roadmap to ensure continued model adaptation to local data distributions.
\section{Architectural Reflections}

The FastAPI/SQLAlchemy monolithic architecture proved highly appropriate
for the MVP development context. FastAPI's automatic OpenAPI schema
generation from Pydantic type annotations eliminated significant API
documentation overhead. SQLAlchemy's async session interface
(\texttt{AsyncSession} with \texttt{asyncpg}) enabled genuinely
non-blocking database queries, resulting in measurably lower latency under
concurrent load compared to synchronous ORM patterns. The combination of
FastAPI and SQLAlchemy is demonstrably well-suited to an ML-serving
application where database queries and model inference must be interleaved
without blocking the event loop.

\section{Kazakhstan-Specific Considerations}

Data residency compliance was achieved through exclusive use of QazCloud
infrastructure. All PostgreSQL data and ML model artefacts are stored within 
Kazakhstan's territorial boundaries, satisfying the requirements of 
Law~No.~94-V \citep{kazakhstanlaw94v}. This represents a structural 
differentiator relative to all five incumbent CRM systems analysed in 
\cref{sec:existing_systems}.

The pricing analysis indicates that TinyCRM's target subscription price
of approximately KZT~3,000--7,000 per user per month (USD~6.50--15) is
financially viable at 50-user scale, given QazCloud infrastructure costs
of approximately USD~80--120 per month for the production virtual machine
and managed database services. This compares favourably with Salesforce's
minimum tier of USD~25 per user per month, validating the project's
cost-effectiveness rationale for the target market segment.

\section{Limitations and Threats to Validity}

Several limitations constrain the conclusions drawn from this project:

\begin{itemize}
  \item \textbf{External validity (ML):} Models trained on publicly
  available, non-Kazakhstani datasets may not generalise to local CRM
  data without domain adaptation or retraining.

  \item \textbf{Construct validity:} SUS scores measure perceived
  usability but not objective task performance or error rates. A full
  usability study with think-aloud protocols and task completion time
  measurements would strengthen the evaluation.

  \item \textbf{Security:} No independent penetration testing was
  conducted. SQL injection, XSS, and CSRF protections are implemented via
  FastAPI and SQLAlchemy defaults but have not been audited.

\end{itemize}
